Untrusted B2B Collaboration using the Blockchain

### 2018-07-18 paper/paper.tex
Reformat, small structure changes

Given the architecture, we will now discuss the implementation of a) the contracts used in the system, and b) the tools for interacting with the system.

@@

@@

\subsection{eth\_admin}

@@

\subsection{armadillo}

>>>>

Given the architecture, we will now discuss the implementation of the contracts used in the system.
Afterwards, we will shortly describe the tools we built for interacting with the system.

@@

\subsubsection{Process Contracts}

@@

\subsection{Tools}

\subsubsection{eth\_admin}

@@

\subsubsection{armadillo}
